Application for Rethinking Foundations of Physics 2017

### 2017-01-15 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Proposed Question} Start updating...

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question is whether there is a ``real'' infinitely-precise quantum
state that is being approximated and that can be more and more accurately
described given more and more resources.

>>>>

Quantum machines is a theory of probability, which is computed by
the Born rule~\cite{Born1983,Mermin2007,Jaeger2007} and is used
to be considered infinite precise and objective. If we changed the
quantum probability to a subjective probability model, which is bound
to be approximations represented by intervals of confidence, then

quantum states themselves can only be discussed within intervals of
confidence. This raises an important philosophical question with immense
practical relevance in the context of quantum computing. The question
is whether there is a ``real'' infinitely-precise quantum state
that is being approximated and that can be more and more accurately
described given more and more resources.
